---
output: github_document
---

[![stability-deprecated](https://img.shields.io/badge/stability-deprecated-red.svg)](https://github.com/emersion/stability-badges#deprecated)
[![Travis build status](https://travis-ci.org/wlandau/drake.future.lapply.staged.svg?branch=master)](https://travis-ci.org/wlandau/drake.future.lapply.staged)
[![Test coverage](https://codecov.io/github/wlandau/drake.future.lapply.staged/coverage.svg?branch=master)](https://codecov.io/github/wlandau/drake.future.lapply.staged?branch=master)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(drake.future.lapply.staged)
```

# Staged parallelism for the drake R package

With staged parallelism, `drake` partitions the dependency graph into stages of conditionally independent targets and processes each stage with semi-transient parallel workers. This functionality is already deprecated, and it will be removed at some point later on.

## Installation

```{r installstaged, eval = FALSE}
library(remotes)
install_github("ropensci/drake")
install_github("wlandau/drake.future.lapply.staged")
```

## Usage

We begin with a `drake` project.

```{r beginstaged}
library(drake.future.lapply.staged)
plan <- drake_plan(x = rnorm(100), y = mean(x), z = median(x))

plan
```

First, create a `future` plan. See the [`future` README](https://github.com/HenrikBengtsson/future/blob/master/README.md) and [`future.batchtools` README](https://github.com/HenrikBengtsson/future.batchtools/blob/master/README.md) for guidance, and consult tables [here](https://github.com/HenrikBengtsson/future/blob/master/README.md#controlling-how-futures-are-resolved) and [here](https://github.com/HenrikBengtsson/future.batchtools/blob/master/README.md#choosing-batchtools-backend) for options for your plan.

```{r introstaged}
library(future)
plan(multiprocess)
```

Next, run your `drake` project.

```{r rundrake}
library(drake.future.lapply.staged)
make(plan, parallelism = backend_future_lapply_staged, jobs = 2)
```

```{r cleanup, echo = FALSE}
unlink(".drake", recursive = TRUE)
```